%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{url}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.345in}
\addtolength{\evensidemargin}{-0.345in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.65in}
\addtolength{\textheight}{1.0in}

\setlength{\footskip}{4.09pt}   % don't understand

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNornal}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingEdu}[6]{
  \vspace{-1pt}
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingNoTitle}[2]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      %\textbf{#1} & #2 \\
      \textit{\small#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemNormal}[1]{\resumeItemNornal{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Quoc-Bao Nguyen}} \\ %& \textit{Built by Latex, Docker. Deployed by Github Pages} \\
   Engineer & \href{https://github.com/baonq-me/resume}{github.com/baonq-me/resume} \textit{(Mar 2025)}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
   \resumeSubheadingEdu
      {University of Science, Ho Chi Minh City}{}
      {Bachelor in Computer Science, Honors Program for talented students}{2014 -- 2018}
      {Graduate thesis: Research and Application of the Homomorphic Encryption Scheme Boneh--Goh--Nissim}{}
      
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Working Experience \textit{(7 years, 4 months)}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Zalo}{Oct 2021 - Present \textit{(3 years, 5 months)}}
      {Senior Software Engineer - Zalo Technical Group - Security \& Operations}{}
      \resumeItemListStart
        \resumeItem{Security Operation Center (SOC)}
          {Build SOC from scratch that processes/stores billions of security events daily. Build \b{Web app firewall} from scratch. Stack: Nginx+lua, Kafka, ElasticSearch, PostgreSQL, Grafana.}       
        \resumeSubItemNormal
          {Mentor, Zalo Tech Fresher 2022. Zalo - Fulbright Leadership Development Program 2022, first batch. Top 20 ZA Challenge 2023 (top 2\%). Most beloved Technical Sharing Series 2024 for a topic related to ARM server CPU.}
      \resumeItemListEnd

    \resumeSubheading
      {Tiki}{Dec 2020 - Oct 2021 \textit{(11 months)}}
      {Software Development Engineer I - Marketplace Department}{}
      \resumeItemListStart
        \resumeItem{Seller Operation}
          {Extend backend APIs to handle complex and fast-growing e-commerce businesses.}    
      \resumeItemListEnd
      
    \resumeSubheading
      {VNG Cloud}{May 2019 - Mar 2021 \textit{(1 year, 10 months)}}
      {Software Engineer - Cloud Call Center}{}
      \resumeItemListStart
        \resumeItem{Key team member}
          {Support other teams and customers as well as maintain, update, design, and implement new features and train new members for the product.}
        \resumeItem{Call Routing}
          {Build a virtual agent that routes inbound calls to the correct operators based on voice interaction.}
        \resumeItem{Awards}
          {Best employees of the quarter (Q4/2019, Q3/2020). Report several security issues to others.}
      \resumeItemListEnd

    \resumeSubheading
      {Vietnix JSC}{Mar 2017 - Apr 2018 \textit{(1 year, 2 months)}}
      {System Intern - R\&D}{}
      \resumeItemListStart
        \resumeItem{SIEM project}
          {Configure OSSEC agent and AlienVault OSSIM by writing alert rules using regex.}
        \resumeItem{OpenStack and OpenNebula}
          {R\&D solution for use as a public cloud service.}
        \resumeItem{WHMCS}
        {Write a provisioning module in PHP for WHMCS to integrate with OpenNebula.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Open source projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/cve-search/cve-search/releases/tag/v5.0.0}{cve-search}}
      {Contribute bug fixes and improvements for 5.0 release. \href{https://github.com/cve-search/cve-search/releases/tag/v5.0.0}{https://github.com/cve-search/cve-search}}
    %\resumeSubItem{\href{https://github.com/baonq-me/bgn}{Graduation Thesis}}
    %  {Somewhat homomorphic encryption over elliptic curve using the BGN cryptosystem.}
    \resumeSubItem{\href{https://github.com/search?q=repo\%3Asignalwire\%2Ffreeswitch\%20baonq5&type=code}{FreeSwitch}}
      {\href{https://github.com/search?q=repo\%3Asignalwire\%2Ffreeswitch\%20baonq5&type=code}{Help FreeSwitch download files from AWS S3 service using AWS Signature version 4.}}
      
\resumeSubHeadingListEnd


\section{Skills / Experience}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {Primarily use Java, familiarity in Lua, Python, SQL, limited experience in Go.}
    \resumeSubItem{Technical Skills}
      {Linux, Nginx, Graylog, MySQL/MongoDB, ElasticSearch, Kafka, VictoriaMetrics/Grafana, FreeSwitch, Proxmox/OpenNebula, K8s (via snap) + Wireguard, Ceph, Arduino/Raspberry Pi.}
    \resumeSubItem{Proficient Areas}
      {Server hardware (compute/network/storage), Cloud, low latency GPU infer at large scale, VoIP.}
\resumeSubHeadingListEnd
  
\section{Hobbies}
  \resumeSubHeadingListStart
    \resumeSubItemNormal
      {Research computer science topics, focusing on design and concepts of protocols and distributed systems.}
  \resumeSubItemNormal
      {Doing electronic projects using Arduino/Raspberry Pi. Owner of physical rack servers and a QSFP28 Cisco switch.}
\resumeSubHeadingListEnd

\section{Social activities}
  \resumeSubHeadingListStart
    \resumeSubItemNormal
      {Organize a full-day tech event named Arduino Day yearly (2015-2019, 2023) that attracts hundreds of people.}
    \resumeSubItemNormal
      {Speak at BarCamp Saigon, Arduino Day, FOSSASIA Summit, VNG Security Day, OpenInfra Day (organizer team),...}
    %\resumeSubItemNormal
    %  {Attend track Science \& Technology Innovation in Vietnam Summer School in Development 2020 at ICISE, Binh Dinh.}
    \resumeSubItemNormal
      {Attended project: \href{https://thaythuocdonghanh.vn}{Thay thuoc dong hanh} - Certificate awarded by Ministry of Science and Technology for providing technical support in the "Thay thuoc dong hanh" network supporting over 500K Covid-19 F0 patients since Aug 2021.}
    \resumeSubItemNormal
    {Certificate from Vietnam Association for Information Processing for contributions to Vietnam OSS community, 2024.}
\resumeSubHeadingListEnd

\section{References}
    \small{\href{https://hackaday.com/2019/06/06/fablab-saigon-celebrates-a-belated-arduino-day/}{https://hackaday.com/2019/06/06/fablab-saigon-celebrates-a-belated-arduino-day/}}
    \small{\href{https://superuser.openinfra.dev/articles/viet-openinfra-user-group-holds-its-30th-meetup/}{https://superuser.openinfra.dev/articles/viet-openinfra-user-group-holds-its-30th-meetup/}}\newline
    \small{\href{https://thanhnien.vn/vi-sao-nhieu-nguoi-me-arduino-nen-tang-duoc-cho-la-tien-than-cua-giao-duc-stem-185230704165819482.htm}{https://thanhnien.vn/arduino.html}}
   
%-------------------------------------------
\end{document}
